---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# neami

<!-- badges: start -->
<!-- badges: end -->

The goal of neami is to support the production of high-quality research and evaluation 
reports within the organisation. It borrows functionality from the BBC bbplot](https://github.com/bbc/bbplot) package
and the [ochRe](https://github.com/hollylkirk/ochRe) package. 

## Installation

You can install the development version of neami like so:

``` r
remotes::install_github("Lingtax/neami")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning=FALSE}
library(neami)
library(tibble)
library(ggplot2)
library(patchwork)
## basic example code
df <-  tibble(x = 1:8, y = 8:1)
p1 <- ggplot(df, aes(x, y)) +
  geom_point()

(p1 +labs(title = "Unstyled")) + (p1 +labs(title = "Neami styled") + theme_neami())
```


For final publication, graphs can be finalised with a Neami logo and source of data.

```{r finalise_plot, warning=FALSE}
p1 <- p1 + labs(title = "A Neami styled plot", 
                subtitle = "with a subtitle") + theme_neami()
finalise_plot(p1, source = "Made-up data", save = FALSE)
```

## Managing fonts. 

Neami standards are in the style guide 
To enable the fonts, install Utopia Std and Brandon text, then run:
```{r fonts, eval=FALSE}
install.packages(extrafont)
library(extrafont)
font_import()
loadfonts(device = "win")

```

Then when you require non-native fonts, simply load the `extrafonts` package.

```{r}
library(extrafonts)
```

See the [extrafonts github page](https://github.com/wch/extrafont) for more details.
