---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
<!-- badges: end -->

The goal of the neami package is to support the production of high-quality research and evaluation 
reports within the organisation. 

## Installation

You can install the development version of neami like so:

``` r
remotes::install_github("Lingtax/neami")
```

## Examples

A core set of functions exist to support graphs in brand consistent formats. 

```{r theming, warning=FALSE, fig.height=10}
library(neami)
library(tibble)
library(ggplot2)
library(patchwork)
## basic example code
df <-  tibble(x = 1:8, y = sample(8:1, 8),  colour = 1)
p1 <- ggplot(df, aes(x, y, colour = colour)) +
  geom_line()  +
  guides(colour = FALSE)
  

(((p1 + labs(title = "Unstyled"))  + plot_spacer()) / 
  ((p1 +labs(title = "Neami styled (light)") + theme_neami() + scale_colour_neami_c("core_qual")) +
  (p1 +labs(title = "Neami styled (dark)") + theme_neami_dark() + scale_colour_neami_c("core_qual_light")) 
     ))
```

Other functions exist to support common analysis and reporting tasks including calculation and reporting of group level change and individual reliable change metrics. 

```{r}
showtext::showtext_auto()
test <- data.frame(person = 1:30, pre = rnorm(30, 30, 9.2), post = rnorm(30, 22, 9.2))

add_k10_change(test, pre, post) %>% janitor::tabyl(rel_k10_change)

# Caption a t-test 
caption_ttest(t.test(test$pre, test$post, var.equal = TRUE))

test %>% tidyr::pivot_longer(cols = pre:post) %>% 
paired_t_plot(x= name, y = value, group = person)

```


